Group 9 Paper

### 2021-12-16 paper.Rmd
repr tree
Reprtree

In the paper Banerjee, et al. discuss how to choose the most representative tree in an ensemble, which is done by finding the average distance between one tree and all other trees in the ensemble. Banerjee, et al. discusses several types of distance in this paper only one of them was used, as it was already implemented in R package. This measure captures the similarities between the predictions, in that 2 trees are similar if they have the same predictions outcomes

>>>>

In the paper Banerjee, et al. discuss how to choose the most representative tree in an ensemble, which is done by finding the average distance between one tree and all other trees in the ensemble. Banerjee, et al. discusses several types of distance in this paper only one of them was used, as it was already implemented in a R package. This measure captures the similarities between the predictions, in that 2 trees are similar if they have the same predictions for all subjects, this is defined by Banerjee, et al as :
$d_2(T_1,T_2)=\frac{1}{n}\sum_{i=1}^n(\hat{y}_{1i}-\hat{y}_{2i})^2$, if the trees perfectly similar, the distance $d_2(T_1,T_2)$ is equal 0. For for finding the representative tree we used the package "reptree", and using it on this random forests we got the following tree:
